### 2015-09-23 doc/manual/inputParameters.tex
Implemented includeRadialExBDrive

\param{nonlinear}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If true, certain terms that are nonlinear in the unknowns will be included in the kinetic equation.
Newton's method will be used to solve the nonlinear system, meaning that the usual linear solve in \sfincs~must
be iterated several times.
Running with {\ttfamily nonlinear}=\true requires \parlink{includePhi1}=\true
}

>>>>

\param{includeRadialExBDrive}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If true, the radial $\vect{E}\times\vect{B}$ term $(\vect{v}_{E} \cdot\nabla\psi)f_{Ms} [(1/n_s)(dn_s/d\psi) + (x_s^2-3/2)(1/T_s)(dT_s/d\psi)]$
will be included in the kinetic equation. This is one of the terms considered in Ref \cite{Regana2013} which
should be unimportant for the main ions but which may be important for impurities.
Use of this option requires \parlink{includePhi1}=\true, since the radial $\vect{E}\times\vect{B}$ drift
arises due to $\Phi_1$.
}

\param{nonlinear}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If true, the term
$-(Z_s e/m) (\nabla_{||} \Phi_1) (\partial f_{s1}/\partial v_{||})_\mu$ will be included
in the kinetic equation.  This is one of the terms considered in Ref \cite{Regana2013} which
should be unimportant for the main ions but which may be important for impurities.
This term is nonlinear in the unknowns $f_{s1}$ and $\Phi_1$.
Newton's method will be used to solve the nonlinear system, meaning that the usual linear solve in \sfincs~must
be iterated several times.
Running with {\ttfamily nonlinear}=\true requires \parlink{includePhi1}=\true
}
